---
title: 'Course Project: Shiny Application and Reproducible Pitch'
author: "Nupur Sinha"
date: "7/17/2020"
output:
  ioslides_presentation: default
  slidy_presentation: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Auto Analysis Report

ISLR Dataset Auto Data Analysis Report

## Application Overview

- Cars can be analysed using several parameters.
- Some of the common parameters are gas mileage, engine horsepower, cylinders, displacement, weight, acceleration.
- This report enables to predict the mpg for a car based on number of cylinders, horsepower and acceleration inputted by the user.

## Slide with Complete Reporting Appliaction

Click the Below Link for the Application.

https://ns92.shinyapps.io/Auto_Course9/

Click the link below for compiled project files on gitub repo.

https://github.com/nsinha08/Course9

## Data Used

The data used for this application is ISLR Auto data set. It has information about gas mileage, engine horsepower, cylinders, displacement, weight, acceleration, model year, car origin, vehicle name for 392 vehicles.

```{r, echo=TRUE}
library(ISLR)
data(Auto)

summary(Auto)
str(Auto)
```